\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\vspace{1.5cm}
\paragraph{}\ \ \ \ Small-scale vendors face significant challenges in competing with large retail chains due to limited purchasing power, inefficient logistics, and restricted access to financial services. These barriers often hinder their ability to manage demand fluctuations and make informed business decisions, threatening their long-term sustainability. This project aims to address these issues by developing a comprehensive platform that empowers small vendors through collaborative purchasing, optimized logistics, and data-driven decision-making. By enabling vendors to combine orders, the platform facilitates bulk purchasing, unlocking competitive discounts and cost savings. Advanced algorithms optimize logistics by streamlining delivery routes, thereby reducing transportation costs and enhancing operational efficiency. Among the optimization methods evaluated, the Environment Adaptive Genetic Algorithm (EAGA) consistently outperformed the Environment Adaptive Ant Colony Optimization (EAACO), delivering more efficient route planning and faster convergence. For order grouping, a hybrid clustering strategy was introduced: while DBSCAN proved effective for smaller datasets, the GA-DBSCAN model achieved higher clustering quality on larger and more complex distributions by dynamically adjusting parameters. These features empower vendors to make strategic decisions that align with market demands and their business goals. The ultimate goal is to level the playing field for small vendors, enabling them to compete effectively with larger retail chains while fostering sustainable growth in local economies. The deliverables of this project include a fully functional platform supporting vendor collaboration and an optimized logistics module to reduce operational costs. By promoting economic resilience, enhancing competitiveness, and driving sustainable development, this project seeks to strengthen the local vendor ecosystem and contribute to the overall development of communities.