\addcontentsline{toc}{chapter}{Appendix B: Vision, Mission, PO, PSO, and CO}
\chapter*{}
\paragraph\
\vspace{75mm}
\begin{center}
	\textbf{\huge{Appendix B: }}
	\textbf{\huge{Vision, Mission, PO, PSO, and CO}}
\end{center}
%	\includepdf[pages=-]{2.pdf}
\clearpage
\clearpage
\newpage
%\cleardoublepage
\thispagestyle{empty}
\begin{center}
	\Large \bfseries RAJAGIRI SCHOOL OF ENGINEERING AND TECHNOLOGY (AUTONOMOUS)
\end{center}
\vspace{0.5cm}
\renewcommand{\baselinestretch}{1.2}\normalsize
\noindent\textbf{Vision}
\begin{tcolorbox}[colback=white, colframe=black, rounded corners, width=\textwidth]
	To evolve into a premier technological and research institution, molding eminent professionals with creative minds, innovative ideas and sound practical skill, and to shape a future where technology works for the enrichment of mankind.
\end{tcolorbox}

\noindent\textbf{Mission}
\begin{tcolorbox}[colback=white, colframe=black, rounded corners, width=\textwidth]
	To impart state-of-the-art knowledge to individuals in various technological disciplines and to inculcate in them a high degree of social consciousness and human values, thereby enabling them to face the challenges of life with courage and conviction.
\end{tcolorbox}

\vspace{1.5cm}
\begin{center}
	\Large \bfseries DEPARTMENT OF COMPUTER SCIENCE AND BUSINESS SYSTEMS
\end{center}
\vspace{0.5cm}
\noindent\textbf{Vision}
\begin{tcolorbox}[colback=white, colframe=black, rounded corners, width=\textwidth]
	To evolve into a department of excellence in information technology by the creation and exchange of knowledge through leading-edge research, innovation and services, which will in turn contribute towards solving complex societal problems and thus building a peaceful and prosperous mankind.
\end{tcolorbox}

\noindent\textbf{Mission}
\begin{tcolorbox}[colback=white, colframe=black, rounded corners, width=\textwidth]
	To impart high-quality technical education, research training, professionalism and strong ethical values in the young minds for ensuring their productive careers in industry and academia so as to work with a commitment to the betterment of mankind.

\end{tcolorbox}


%	To inspire and nurture students, with up-to-date knowledge in Computer Science and Engineering, ethics, team spirit, leadership abilities, innovation and creativity to come out with solutions meeting societal needs. \\ \\
\newpage
\noindent\textbf{Programme Outcomes (PO)} \\
Engineering Graduates will be able to:
\begin{enumerate}
	\item {Engineering Knowledge:} Apply the knowledge of mathematics, science, engineering fundamentals, and an engineering specialization to the solution of complex engineering problems.
	\item {Problem Analysis:} Identify, formulate, review research literature, and analyze complex engineering problems reaching substantiated conclusions using first principles of mathematics, natural sciences, and engineering sciences.
	\item {Design/Development of Solutions:} Design solutions for complex engineering problems and design system components or processes that meet the specified needs with appropriate consideration for public health and safety, and the cultural, societal, and environmental considerations.
	\item {Conduct Investigations of Complex Problems:} Use research-based knowledge including design of experiments, analysis and interpretation of data, and synthesis of the information to provide valid conclusions.
	\item {Modern Tool Usage:} Create, select, and apply appropriate techniques, resources, and modern engineering and IT tools including prediction and modeling to complex engineering activities with an understanding of the limitations.
	\item {The Engineer and Society:} Apply reasoning informed by the contextual knowledge to assess societal, health, safety, legal, and cultural issues and the consequent responsibilities relevant to the professional engineering practice.
	\item {Environment and Sustainability:} Understand the impact of the professional engineering solutions in societal and environmental contexts, and demonstrate the knowledge of, and need for sustainable development.
	\item {Ethics:} Apply ethical principles and commit to professional ethics and responsibilities and norms of the engineering practice.
	\item {Individual and Team Work:} Function effectively as an individual, and as a member or leader in teams, and in multidisciplinary settings.
	\item {Communication:} Communicate effectively on complex engineering activities with the engineering community and with society at large, such as, being able to comprehend and write effective reports and design documentation, make effective presentations, and give and receive clear instructions.
	\item {Project Management and Finance:} Demonstrate knowledge and understanding of engineering and management principles and apply these to one’s own work, as a member and leader in a team. Manage projects in multidisciplinary environments.
	\item {Life-long Learning:} Recognize the need for, and have the preparation and ability to engage in independent and lifelong learning in the broadest context of technological change.
\end{enumerate}

\subsection*{Programme Specific Outcomes (PSO)}

A graduate of the Computer Science and Business Systems Programme will:
\begin{itemize}
	\item \textbf{PSO 1: Programming and Software Development Skills} \\
	      Demonstrate ability to analyze, design, and implement software solutions incorporating various programming concepts.
	\item \textbf{PSO 2: Engineering Management and Collaboration} \\
	      Comprehend professional, managerial, and financial aspects of business and collaborate on the design, implementation, and integration of engineering solutions.
	\item \textbf{PSO 3: Decision-Making and Analytical Techniques in Engineering and Business} \\
	      Create, select, and apply appropriate techniques and business tools, including prediction and data analytics, for complex engineering activities and business solutions.
\end{itemize}

\subsection*{Course Outcomes (CO)}

After successful completion of the course, the students will be able to:
\begin{itemize}
	\item {CO1:} Model and solve real-world problems by applying knowledge across domains (Cognitive knowledge level: Apply).
	\item {CO2:} Develop products, processes, or technologies for sustainable and socially relevant applications (Cognitive knowledge level: Apply).
	\item {CO3:} Function effectively as an individual and as a leader in diverse teams and to comprehend and execute designated tasks (Cognitive knowledge level: Apply).
	\item {CO4:} Plan and execute tasks utilizing available resources within timelines, following ethical and professional norms (Cognitive knowledge level: Apply).
	\item{CO5:} Identify technology/research gaps and propose innovative/creative solutions (Cognitive knowledge level: Analyze).
	\item {CO6:} Organize and communicate technical and scientific findings effectively in written and oral forms (Cognitive knowledge level: Apply).
\end{itemize}